Matching bullets

### 2015-11-20 imaging-paper.Rnw
Remove duplicated introduction
start on automatic alignment

%% the only exception to this rule is the \firstsection command
\firstsection{Introduction}

@@

\section{Introduction}
Bullet matching is a process in forensic science done to determine whether two bullets were fired from the same gun barrel. This process has broad applicability in terms of the conviction of criminals in the United States criminal justice system. Ballistics identification has long been considered an accepted and reliable procedure, but in the past ten years has undergone some more significant scrutiny. In 2005, in \emph{United States vs. Green}, the court ruled that the expert could not confirm that the bullet casings came from a specific weapon with certainty, but could merely describe other casings which are similar. Further court cases in the late 2000s expressed caution about the use of ballistics identification evidence.

@@

<<circlefits2, echo=FALSE, fig.width=10, fig.height=7, out.width='\\linewidth', warning=FALSE, fig.cap='Circle fit for each cross section of bullet 2, with part 2 of bullet 1 overlayed.', fig.pos='H'>>=
qplot(y, resid, data=subset(db2, x <= 80*1.5625^2 & x >=75*1.5625^2), colour=factor(x), geom="line", size=I(1)) + 
  facet_wrap(~part) + scale_colour_brewer(palette="Paired") +
  theme_bw() + theme(legend.position="bottom") + 
  geom_line(aes(y, resid, group =x), colour="black", size=1, alpha=0.2, 
             data = filter(db1, part==2, x <= 80*1.5625^2, x >=75*1.5625^2)[,c("y", "resid", "x")]) + ggtitle("Part 2 of Bullet 1 in black")
@

@@

@@

\includegraphics[width=\columnwidth]{images/side-by-side-manual-match.png}
\caption{\label{fig:manualmatch}\hh{Manually adjusted side-by-side comparison of two lands from different bullets.}}
\end{figure}

\begin{figure}
\includegraphics[width=\columnwidth]{images/matchup-rgl.png}
\caption{\label{fig:manualmatch}\hh{Different view of the manually adjusted side-by-side comparison of two lands from different bullets.}}
\end{figure}

\section{Application}

>>>>

%% the only exception to this rule is the \firstsection command

\firstsection{Introduction}

@@

Bullet matching is a process in forensic science done to determine whether two bullets were fired from the same gun barrel. This process has broad applicability in terms of the conviction of criminals in the United States criminal justice system. Ballistics identification has long been considered an accepted and reliable procedure, but in the past ten years has undergone some more significant scrutiny. In 2005, in \emph{United States vs. Green}, the court ruled that the expert could not confirm that the bullet casings came from a specific weapon with certainty, but could merely describe other casings which are similar. Further court cases in the late 2000s expressed caution about the use of ballistics identification evidence.

@@

<<circlefits2, echo=FALSE, fig.width=10, fig.height=7, out.width='\\linewidth', warning=FALSE, fig.cap='Circle fit for each cross section of bullet 2, with part 2 of bullet 1 overlayed.', fig.pos='H', cache=TRUE>>=
qplot(y, resid, data=subset(db2, x <= 80*1.5625^2 & x >=75*1.5625^2), colour=factor(x), geom="line", size=I(1)) + 
  facet_wrap(~part) + scale_colour_brewer(palette="Paired") +
  theme_bw() + theme(legend.position="bottom") + 
  geom_line(aes(y, resid, group =x), colour="black", size=1, alpha=0.2, 
             data = filter(db1, part==2, x <= 80*1.5625^2, x >=75*1.5625^2)[,c("y", "resid", "x")]) + ggtitle("Part 2 of Bullet 1 in black")
@

@@

\section{Approach to automatic matching}
\hh{XXX all tentative}
Applying the  loess fit to a range of different surface cross cuts (see Figures~\ref{fig:manualmatch} and Figure~\ref{fig:manualmatch}, with cross cuts from 50 to 150) shows the striation marks across two bullets. Cross cuts of bullet 1 are shown on the left (cross cuts with values below 100) and cross cuts of bullets 2 are shown on the right (cross cuts with values above 100). A lot of the striation marks align, allowing for an easy visual assessment of the shared similarities between the two bullets.

@@

\includegraphics[width=\columnwidth]{images/side-by-side-manual-match.png}
\caption{\label{fig:manualmatch}\hh{Manually adjusted side-by-side comparison of land five of bullet 1 and land 1 of bullet 2.}}
\end{figure}

\begin{figure}
\includegraphics[width=\columnwidth]{images/matchup-rgl.png}
\caption{\label{fig:manualmatch}\hh{Different view of the manually adjusted side-by-side comparison of land five of bullet 1 and land 1 of bullet 2.}}
\end{figure}

\section{Application}
We've implemented a web interface to automate many of the steps outlined in the previous section. The web interface, developed using Shiny[ref], allows a user to upload two x3p files representing scans of a bullet between two grooves. A 3D viewer, using Plotly[ref], allows the user to rotate and zoom to examine surface features of the images. A screenshot of the application is available in Figure \ref{fig:app}.

\begin{figure*}
\includegraphics[width=\textwidth]{images/app.png}
\caption{\label{fig:app}{Screenshot of the web interface for analyzing bullet images.}}
\end{figure*}
